Everything I know about Subset Sum Reconfiguration

### 2013-07-19 notes/ssr.tex
Add an explicit mention of one area of uncertainty
Mark the other place the same issue arises

\noindent On the other hand, the instances constructed in Propositions~\ref{prop:element-moves-a-lot} and~\ref{prop:quadratic-bound} have a property that makes them easy to recognise as solvable without the need to construct an actual solution.
\begin{lemma}\label{lemma:reduction}
    Suppose we have an SSR instance with element set $E$, threshold $k$ and capacity $c$. By abuse of notation we shall also refer to the whole instance as $E$. Let $a$ and $z$ be elements of minimal and maximal weight respectively. If $w(z) > c-k$ or $w(a) < c-k-w(z) + 2$ then either $E$ is trivially unsolvable or else there is an element $e\in E$ and a (smaller) instance with element set $E' = E-\{e\}$ that is equivalent to the original in the sense that $E'$ is solvable iff $E$ is.
\end{lemma}
\begin{proof}
    Let $e$ be any element that has weight $z$.

    If $w(z) > c - k$ then our element $z$ cannot move. If $z$ moves between the start and target packings, then $E$ is trivially unsolvable. Otherwise we let $E' = E-\{z\}$. If $z$ is inside in both the start and target packing, let the threshold and capacity of our new instance be $k' = k-w(z)$ and $c' = c-w(z)$, and remove $z$ from the start and target configurations. If $z$ is outside in both the start and target, let $k'=k$ and $c'=c$. Every solution of $E'$ is a solution of $E$, and vice versa -- by adding $z$ to all packings in the solution sequence in the former case, or by literally using the same solution sequence in the latter.

    If $w(a) < c-k-w(z) + 2$ then let $E' = E-\{a\}$. Look at whether or not $a$ belongs to the start configuration: if it does, let $k'=k-w(a)$ and $c'=c$; if not, let $k'=k$ and $c'=c+w(a)$. In both cases we have $c'-k' = c-k+w(a)$. Any solution of $E$ can be converted to a solution of $E'$ just by removing element $a$ from all packings in the sequence and eliminating adjacent duplicates. The interesting part is the converse, converting a solution of $E'$ into a solution of $E$. Let $A_0', \dots, A_m'$ be a sequence of packings that solves $E'$. We shall show how to insert element $a$, with some additional moves of $a$, to obtain a solution of $E$.

>>>>

\noindent On the other hand, the instances constructed in Propositions~\ref{prop:element-moves-a-lot} and~\ref{prop:quadratic-bound} have a property that makes them easy to recognise as solvable without the need to construct an actual solution. (The details need some work here, but I think the basic idea is okay.)
\begin{lemma}\label{lemma:reduction}
    Suppose we have an SSR instance with element set $E$, threshold $k$ and capacity $c$. By abuse of notation we shall also refer to the whole instance as $E$. Let $a$ and $z$ be elements of minimal and maximal weight respectively. If $w(z) > c-k$ or $w(a) < c-k-w(z) + 2$ then either $E$ is trivially unsolvable or else there is an element $e\in E$ and a (smaller) instance with element set $E' = E-\{e\}$ that is equivalent to the original in the sense that $E'$ is solvable iff $E$ is.
\end{lemma}
\begin{proof}
    Let $e$ be any element that has weight $z$.

    If $w(z) > c - k$ then our element $z$ cannot move. If $z$ moves between the start and target packings, then $E$ is trivially unsolvable. Otherwise we let $E' = E-\{z\}$. If $z$ is inside in both the start and target packing, let the threshold and capacity of our new instance be $k' = k-w(z)$ [TODO: what if $k-w(z) < 0$?] and $c' = c-w(z)$, and remove $z$ from the start and target configurations. If $z$ is outside in both the start and target, let $k'=k$ and $c'=c$. Every solution of $E'$ is a solution of $E$, and vice versa -- by adding $z$ to all packings in the solution sequence in the former case, or by literally using the same solution sequence in the latter.

    If $w(a) < c-k-w(z) + 2$ then let $E' = E-\{a\}$. Look at whether or not $a$ belongs to the start configuration: if it does, let $k'=k-w(a)$ and $c'=c$; if not, let $k'=k$ and $c'=c+w(a)$. [TODO: What if $k-w(a) < 0$? This case needs to be considered.] In both cases we have $c'-k' = c-k+w(a)$. Any solution of $E$ can be converted to a solution of $E'$ just by removing element $a$ from all packings in the sequence and eliminating adjacent duplicates. The interesting part is the converse, converting a solution of $E'$ into a solution of $E$. Let $A_0', \dots, A_m'$ be a sequence of packings that solves $E'$. We shall show how to insert element $a$, with some additional moves of $a$, to obtain a solution of $E$.
